QALY Comparisons - `r params$experiment` - `r params$intervention` - `r params$baseline`

### 2024-03-08 minos/outcomes/QALY_comparison2.Rmd
Added some make targets for visualising QALY outputs for Glasgow Scaled simulation runs

---
params:
  experiment: 'default_config/'
  base: 'baseline'
  intervention: '50All'
title: "QALY Comparisons - `r params$experiment` - `r params$intervention` - `r params$baseline`"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

>>>>

---
params:
  experiment: 'default_config/'
  base: 'baseline'
  intervention: ''
title: "QALY Comparisons - `r params$experiment` - `r params$intervention` - `r params$baseline`"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---
